Latent Variable Clustering for Classification of Events in the AT-TPC

### 2020-05-21 doc/Manuscript/article.tex
Updates from Overleaf

\begin{table}
\centering
\caption{Descriptions of number of events in the data used for analysis in this thesis. In principle we can simulate infinite data, but it is both quite simple and not very interesting outside a case for a proof-of-concept}\label{tab:datasets}
\begin{tabular}{lccc}
\toprule
{} & Simulated & Full & Filtered \\
\midrule
Total &  $8000$ & $51891$ & $49169$ \\
labelled & $2400$ & $1774$ &  $1582$ \\ 
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{Descriptions of number of events in the data. In principle we can simulate an arbitrary amount of data, but the following quantities were shown to be sufficient for these studies.}\label{tab:datasets}
\begin{tabular}{lccc}
\toprule
{} & Simulated & Full & Filtered \\
\midrule
Total &  $8000$ & $51891$ & $49169$ \\
labelled & $2400$ & $1774$ &  $1582$ \\ 
\bottomrule
\end{tabular}
\end{table}
